CF Registry Analysis

### 2023-10-05 Christine Chan/CF Registry/cf_registry_analysis.qmd
cfrd registry analysis

annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/Data_Raw/CFF19_Annualized_Del1.csv",

@@

data_dict <- readxl::read_excel("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/Data_Raw/Copy of Codes for CFFPR_2018.xlsx")

@@

demogs <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/Data_Raw/CFF19_DemogCFDiag_Del1.csv")

>>>>

annual <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data/Data_Raw/CFF19_Annualized_Del1.csv",

@@

data_dict <- readxl::read_excel("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data/Data_Raw/Copy of Codes for CFFPR_2018.xlsx")

@@

demogs <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data/Data_Raw/CFF19_DemogCFDiag_Del1.csv")
